Estimating Planetary Habitability via Particle Swarm Optimization of CES Production Functions.

### 2018-01-16 docs/report/draft.tex
Iterations are stored for CDHS.

Tables~\ref{tab:cdhscrs} and~\ref{tab:cdhsdrs} record the difference in the CDHS values as estimated by \pso\ and
Stochastic Gradient Ascent for a sample of planets under CRS and DRS respectively. Tables~\ref{tab:ceesacrs}
and~\ref{tab:ceesadrs} record the same for the CEESA scores.

>>>>

Tables~\ref{tab:cdhscrs} and~\ref{tab:cdhsdrs} record the CDHS values for a sample of exoplanets under CRS and DRS
respectively. Tables~\ref{tab:ceesacrs} and~\ref{tab:ceesadrs} record the same for the CEESA scores. All tables also
record the number of iterations taken to converge to a stable $\gbest$ value.
